---
title: "Projects Analytics Dashboard"
format: html
---

## Dashboard Overview

Project summaries with supporting visuals

### 1. Multilingual Campus Resource Guide

#### Guide distributed to 150+ students


```{r}
#| echo: false
# Load required libraries 
library(ggplot2)
library(dplyr)
library(tidyr)


# Data: Students reached with the guide
students_reached <- data.frame(
  Metric = "Students reached\n(orientation week)",
  Count = 152
)

ggplot(students_reached, aes(x = Metric, y = Count, fill = Metric)) +
  geom_col(width = 0.6, fill = "#2c7da0") +
  geom_text(aes(label = paste0(Count, "+")), vjust = -0.5, size = 5) +
  labs(y = "Number of students", x = NULL, 
       title = "Distribution of Trilingual Resource Guide") +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
        plot.title = element_text(hjust = 0.5)) +
  ylim(0, 180)
```

### 2. Team Collaboration Case Study

#### 95% on final report, Peer feedback: 4.8/5 (“kept everyone focused and respected”)

```{r}
#| echo: false

# Data: Grade and peer feedback score
performance <- data.frame(
  Metric = c("Final Grade (%)", "Peer feedback\n(out of 5)"),
  Value = c(95, 4.8)
)

ggplot(performance, aes(x = Metric, y = Value, fill = Metric)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = Value), vjust = -0.5, size = 5) +
  labs(y = "Score", x = NULL,
       title = "Team Performance & Satisfaction") +
  scale_fill_manual(values = c("#2c7da0", "#5fa8c9")) +
  theme(legend.position = "none") +
  ylim(0, 105)
```

Key outcomes:

- Team completed simulation 2 days early

- 95% on final report

- Peer feedback: 4.8/5 (“kept everyone focused and respected”)

Skills: Conflict mediation • Meeting facilitation • Documentation • Adaptability


### 3. Rancho Cucamonga High School Alumni Panel

#### 40+ high school students attended, 92% felt more confident about applying to college

```{r}
#| echo: false

# Data: Attendance and confidence improvement
impact <- data.frame(
  Category = c("Attendance\n(students)", "Confidence increase\n(post‑event survey)"),
  Percentage_or_Count = c(40, 92)
)

# Create a two‑panel visual: one bar for attendance, one for confidence
attendance <- data.frame(Metric = "Attendees", Count = 40)
confidence <- data.frame(Metric = "Felt more confident", Percent = 92)

p1 <- ggplot(attendance, aes(x = Metric, y = Count, fill = Metric)) +
  geom_col(width = 0.5, fill = "#2c7da0") +
  geom_text(aes(label = paste0(Count, "+")), vjust = -0.5, size = 5) +
  labs(y = "Number of students", x = NULL, title = "Event Reach") +
  theme_minimal() +
  ylim(0, 50)

p2 <- ggplot(confidence, aes(x = Metric, y = Percent, fill = Metric)) +
  geom_col(width = 0.5, fill = "#5fa8c9") +
  geom_text(aes(label = paste0(Percent, "%")), vjust = -0.5, size = 5) +
  labs(y = "Percentage (%)", x = NULL, title = "Confidence Boost") +
  theme_minimal() +
  ylim(0, 100)

# Arrange side by side
gridExtra::grid.arrange(p1, p2, ncol = 2)
```



